Effects of Sudakov form factor in\\ the Golec-Biernat W\"usthoff saturation model

### 2022-09-14 Document/Effects of Sudakov form factor in the Golec-Biernat Wusthoff model.tex
plots subplots

 The dipole cross-section $\sigma_{\mathrm{dp}}$ is related to the gluon density and thus contains non-perturbative effects. Therefore, it has to be modelled. In the region of large dipole size $r$, multi-gluon exchange becomes important and the saturation effects come into play. The present study has roots in the Golec-Biernat W\"usthoff (GBW) model of the dipole cross-section \cite{gbw1998}, which describes the saturation effects in a very simple form.
In the next section, two models on which we develop our modified versions, namely the Golec-Biernat W\"usthoff (GBW) model\cite{gbw1998} and the Bartels Golec-Biernat Kowalski (BGK) model\cite{bgk2002}, are briefly summarized.  In sections 3 and 4, a summary of the modification is given. In section 5, the result of fitting to the data from the HERA\cite{hera} is presented. %{\color{blue}correction comment in summary}

@@

%\section{$k_T$ factorization, dipole cross section, unintegrated gluon distribution and more...}
\section{The Sudakov form factor }
In this section, we discuss how the Sudakov form factor is implemented in the above saturation models.%{\color{blue} and introduce unintegrated gluon distribution.}
The dipole cross-section, $\sigma_{\mathrm{dp}}(x, r) $, and the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, are related to each other by %\footnote{it can also be written$\sigma_{\mathrm{dp}}(x,r) = \frac{4 \pi}{3} \int\frac{d^2 k}{k^4} \alpha_s f(x, k^2) \left(1-e^{\pm i \pairdot{k}{r}}\right) $ considering the independence on the direction of $\mathbf{r}$.}
\cite{bgk2002}
\begin{align} 
\sigma_{\mathrm{dp}}(x,r) &= \frac{2 \pi}{3} \int\frac{d^2 \mathbf{k} }{k^2} \alpha_s f(x, k^2) |1-e^{-i \pairdot{k}{r}}|^2,
\label{eq:ugdtosigma}\\
\alpha_s \mathcal{F}(x,k^2) &= \frac{3 }{16 \pi^3}\int d^2 \mathbf{r} e^{i \pairdot{k}{r}}  \nabla^2_{\mathbf{r}} \sigma_{\mathrm{dp}}(x,r),
\label{eq:sigmatougd}
\end{align}
{\color{blue} $|...|^2$ can be seen in Ref.~\cite{bgk2002} Eq.~(15). Expanding \& considering rot. inv. , one can recover $1-e^{-ik\cdot r} $ with a factor 2.} 
where the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, is related to the integrated gluon distribution, $g(x,Q^2)$, by the relation, for large $Q^2$ \cite{bgk2002},%{\color{red}(large Q only? bgk)} 
\begin{equation}
\alpha_s(Q^2) x g(x,Q^2)=\int^{Q^2}_{0} d k^2 \alpha_s \mathcal{F}(x,k^2).
\end{equation}
Following the convention of Ref.~\cite{bgk2002}, we consider an object $\alpha_s\mathcal{F}(x,k^2)\equiv\alpha_s(k^2)\mathcal{F}(x,k^2)$.

@@

\begin{figure}[t]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/dipole-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/dipole-BGK.png}
}
\caption{The dipole cross-section $\sigma_{\mathrm{dp}}$ at $Q^2=650\;\mathrm{GeV^2}$, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
%\label{dipole-bgk}
\label{dipole}
\end{figure}

@@

\begin{figure}[t]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/F2-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/F2-BGK.png}
}
\caption{The structure function $F_2$ , and $x=10^{-2}, 10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
\label{F2}
\end{figure}

\begin{figure}[t]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/gluon-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/gluon-BGK.png}
}
\caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $x=10^{-4}$. Notice the broadening effect of the Sudakov factor.\\Left: GBW, Right: BGK}
\label{fig:gluon}
\end{figure}
\begin{figure}[t]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/gluon-x-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/gluon-x-BGK.png}
}
\caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $k^2=1\mathrm{GeV^2}$. Notice the broadening effect of the Sudakov factor.\\Left: GBW, Right: BGK}
\label{fig:gluon-x}
\end{figure}

@@

\begin{figure}[t]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/critical-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/critical-BGK.png}
}
\caption{Saturation scale $Q_S^2(x)$\\
%\caption{Saturation scale $Q_S^2(x)$  obtained from two different criteria:\\
%$\frac{\partial^2 \sigma }{\partial r^2}=0$ (Curvature) \& $\frac{\partial \alpha_s\mathcal{F}(x,k^2) }{\partial k}=0$ (Peak).\\ 
The line was plotted for $Q^2=650\;\mathrm{ GeV^2}$.\\Left: GBW, Right: BGK }
\label{fig:critical}
\end{figure}

@@

\begin{figure}[H]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/slope-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/slope-BGK.png}
}
\caption{The $x$-slope of $F_2$  at $Q^2=650$GeV, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
\label{slope}
\end{figure}

\begin{figure}[H]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/ww-gluon-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/ww-gluon-BGK.png}
}
\caption{Weizs\"acke-Williams gluon distrubution $\phi=k\int \frac{d^2r}{r^2} e^{-i r\cdot k} \sigma_{\mathrm{dp}}(x,r,Q^2)$.\\Left: GBW, Right: BGK
}
%\label{fig:gluon}
\end{figure}

\begin{figure}[H]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/ww-critical-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/ww-critical-BGK.png}
}
\caption{Saturation scale $Q_s^2(x)$  obtained from the Weiz\"acker-Williams gluon distribution.
The crieria is analogous to Eq.~(\ref{eq:peak}) for $\phi=k\int \frac{d^2r}{r^2} e^{-i r\cdot k} \sigma_{\mathrm{dp}}(x,r,Q^2)$ but with an extra factor 2 as in the original GBW saturation scale.  i.e., $Q_s=2 k_s$.\\Left: GBW, Right: BGK }
%\label{fig:critical}
\end{figure}

\begin{figure}[H]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/FL-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/FL-BGK.png}
}
\caption{Longitudinal structure function $F_L$ at fixed $W=100, 200, 300$ GeV (from bottom to top).
The effects of the Sudakov factor is primarily in the large-$Q^2$ region, lifting up the line for both GBW and BGK models.\\ 
Left: GBW, Right: BGK}
%\label{fig:critical}
\end{figure}

>>>>

The dipole cross-section $\sigma_{\mathrm{dp}}$ is related to the gluon density and thus contains non-perturbative effects. {\color{blue} Therefore, it has to be, to an extent, modelled. Nonetheless, solving appropriate evolution equeations, such as the Balitsky-Kovchegov equation, is computationally expensive, and thus it is useful to have a simple model to describe the saturation effects.}\\
In the region of large dipole size $r$, multi-gluon exchange becomes important and the saturation effects come into play. The present study has roots in the Golec-Biernat W\"usthoff (GBW) model of the dipole cross-section \cite{gbw1998}, which describes the saturation effects in a very simple form.
In the next section, two models on which we develop our modified versions, namely the Golec-Biernat W\"usthoff (GBW) model\cite{gbw1998} and the Bartels Golec-Biernat Kowalski (BGK) model\cite{bgk2002}, are briefly summarized.  In sections 3 and 4, a summary of the modification is given. In section 5, the result of fitting to the data from the HERA\cite{hera} is presented. %{\color{blue}correction comment in summary}

@@

%\section{$k_T$ factorization, dipole cross section, unintegrated gluon distribution and more...}
\section{The Sudakov form factor }
In this section, we discuss how the Sudakov form factor is implemented in the above saturation models. %{\color{blue} and introduce unintegrated gluon distribution.}
The dipole cross-section, $\sigma_{\mathrm{dp}}(x, r) $, and the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, are related to each other by\footnote{it can also be written $\sigma_{\mathrm{dp}}(x,r) = \frac{4 \pi}{3} \int\frac{d^2 k}{k^4} \alpha_s \mathcal{F}(x, k^2) \left(1-e^{\pm i \pairdot{k}{r}}\right) $ considering it only depends on the relative angle between $\mathbf{r}$ and $\mathbf{k}$.}
\cite{bgk2002}
\begin{align} 
\sigma_{\mathrm{dp}}(x,r) &= \frac{2 \pi}{3} \int\frac{d^2 \mathbf{k} }{k^2} \alpha_s \mathcal{F}(x, k^2) |1-e^{-i \pairdot{k}{r}}|^2,
\label{eq:ugdtosigma}\\
\alpha_s \mathcal{F}(x,k^2) &= \frac{3 }{16 \pi^3}\int d^2 \mathbf{r} e^{i \pairdot{k}{r}}  \nabla^2_{\mathbf{r}} \sigma_{\mathrm{dp}}(x,r),
\label{eq:sigmatougd}
\end{align}
%{\color{blue} $|...|^2$ can be seen in Ref.~\cite{bgk2002} Eq.~(15). Expanding \& considering rot. inv. , one can recover $1-e^{-ik\cdot r} $ with a factor 2.} 
where the unintegrated gluon distribution is related to the integrated gluon distribution, $g(x,Q^2)$, by the relation, for large $Q^2$ \cite{bgk2002},%{\color{red}(large Q only? bgk)} 
\begin{equation}
\alpha_s(Q^2) x g(x,Q^2)=\int^{Q^2}_{0} d k^2 \alpha_s \mathcal{F}(x,k^2).
\end{equation}
Following the convention of Ref.~\cite{bgk2002}, we consider an object $\alpha_s\mathcal{F}(x,k^2)\equiv\alpha_s(k^2)\mathcal{F}(x,k^2)$.

@@

\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/dipole-GBW.png}
}
%\resizebox{0.5\textwidth}{!}{
%\includegraphics{./Plots/dipole-BGK.png}
%}
\caption{The dipole cross-section $\sigma_{\mathrm{dp}}$ at $Q^2=650\;\mathrm{GeV^2}$, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
%\label{dipole-bgk}
\label{dipole}
\end{figure}

@@

\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/F2-GBW.png}
}
%\resizebox{0.5\textwidth}{!}{
%\includegraphics{./Plots/F2-BGK.png}
%}
\caption{The structure function $F_2$ , and $x=10^{-2}, 10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
\label{F2}
\end{figure}
\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/slope-GBW.png}
}
\caption{The $x$-slope of $F_2$,  $\lambda_{\mathrm{eff}}=-\frac{\partial \log F_2}{\log x}$, at $Q^2=650$GeV, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
\label{slope}
\end{figure}

\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/gluon-GBW.png}
}
%\resizebox{0.5\textwidth}{!}{
%\includegraphics{./Plots/gluon-BGK.png}
%}
\caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $x=10^{-4}$. Notice the broadening effect of the Sudakov factor.\\Left: GBW, Right: BGK}
\label{fig:gluon}
\end{figure}
\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/gluon-x-GBW.png}
}
%\resizebox{0.5\textwidth}{!}{
%\includegraphics{./Plots/gluon-x-BGK.png}
%}
\caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $k^2=1\mathrm{GeV^2}$. Notice the broadening effect of the Sudakov factor.\\Left: GBW, Right: BGK}
\label{fig:gluon-x}
\end{figure}

@@

\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/critical-GBW.png}
}
%\resizebox{0.5\textwidth}{!}{
%\includegraphics{./Plots/critical-BGK.png}
%}
\caption{Saturation scale $Q_S^2(x)$\\
%\caption{Saturation scale $Q_S^2(x)$  obtained from two different criteria:\\
%$\frac{\partial^2 \sigma }{\partial r^2}=0$ (Curvature) \& $\frac{\partial \alpha_s\mathcal{F}(x,k^2) }{\partial k}=0$ (Peak).\\ 
The line was plotted for $Q^2=650\;\mathrm{ GeV^2}$.\\Left: GBW, Right: BGK }
\label{fig:critical}
\end{figure}

\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/FL-GBW.png}
}
%\resizebox{0.5\textwidth}{!}{
%\includegraphics{./Plots/FL-BGK.png}
%}
\caption{Longitudinal structure function $F_L$ at fixed $W=100, 200, 300$ GeV (from bottom to top).
The effects of the Sudakov factor is primarily in the large-$Q^2$ region, lifting up the line for both GBW and BGK models.\\ 
Left: GBW, Right: BGK}
%\label{fig:critical}
\end{figure}

@@

\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/ww-gluon-GBW.png}
}
%\resizebox{0.5\textwidth}{!}{
%\includegraphics{./Plots/ww-gluon-BGK.png}
%}
\caption{Weizs\"acke-Williams gluon distrubution $\phi=k\int \frac{d^2r}{r^2} e^{-i r\cdot k} \sigma_{\mathrm{dp}}(x,r,Q^2)$.\\Left: GBW, Right: BGK
}
%\label{fig:gluon}
\end{figure}

\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/ww-critical-GBW.png}
}
%\resizebox{0.5\textwidth}{!}{
%\includegraphics{./Plots/ww-critical-BGK.png}
%}
\caption{Saturation scale $Q_s^2(x)$  obtained from the Weiz\"acker-Williams gluon distribution.
The crieria is analogous to Eq.~(\ref{eq:peak}) for $\phi=k\int \frac{d^2r}{r^2} e^{-i r\cdot k} \sigma_{\mathrm{dp}}(x,r,Q^2)$ but with an extra factor 2 as in the original GBW saturation scale.  i.e., $Q_s=2 k_s$.\\Left: GBW, Right: BGK }
%\label{fig:critical}
\end{figure}
